### 2020-06-18 confirm-activity/tex/intro.tex
sync intro with CESC submission

\section{Introduction}
\label{intro}
The NuCypher network~\cite{egorov2017nucypher} is a decentralized key management 
system, encryption, and access control service. It uses proxy re-encryption, namely, the 
Umbral scheme~\cite{umbral2018}, to delegate access to encrypted 
documents through a public network. This network is composed of a set of semi-trusted 
re-encryption servers, or Ursulas, that implement access control policies created by data 
owners, or Alices. Alice supplies each Ursula with re-encryption keys allowing Ursula to transform 
ciphertexts encrypted under Alice's public key into ciphertexts encrypted under the delegatee's, or Bob's,
public key. This enables the latter to decrypt the ciphertext without revealing anything about the
decryption keys or the raw data to the intermediate servers.

Joining the NuCypher network is governed by consensus rules defining the service setup
and the monetary incentives paid to provide the service. In order to join the 
system, Ursula needs to stake an amount of NU tokens for a specific period
which will be released when the pre-specified staking period is over. Alice chooses an
Ursula to hold an access control policy with a probability proportional to the stake this Ursula 
pledged in the system. Therefore, the stake value influences the amount of service load an Ursula
may receive. This stake is also used to punish Ursula financially, by revoking part 
of it, if she cheats and this cheating is detected.

Alice joins the network by creating a policy to be implemented by a 
set of Ursulas. This policy specifies the re-encryption key fragments each Ursula will
need to answer requests coming from Bob(s), as well as the duration of the policy, which 
is basically the timeframe during which Bob is authorized to access Alice's data.  Furthermore,
Alice will lock an amount of Ether into the policy to be used to pay Ursulas for the re-encryption 
service. As noted, Alice is not exposed to the NU token. All that she needs is an Ethereum
wallet, awareness of the NuCypher network architecture to select Ursulas, and knowledge of the
NuCypher rules of preparing access control policies.

Bob, on the other hand, does not deal with currency in the system. It interacts with the storage 
network to retrieve the encrypted data, and with Ursulas in the NuCypher network to request the
re-encryption service.

\subsection{Monetary Incentives in the NuCypher Network}
Ursulas are rewarded for the re-encryption service by using two sources; 
the first is the service fees collected from the policy  
owner Alice, while the second is inflation rewards, i.e., newly minted
NU tokens, coming from the NuCypher network. The latter will be provided during the 
early stage of the network operation to encourage 
adoption. It is expected that these rewards will disappear as the token cap is 
reached, similar to other cryptocurrencies in the space.

Currently, the inflation rewards for each round or period are computed for each Ursula based on the size of her stake given that she confirms to be online during this round. Confirming the status of being online is done by calling a 
simple function in one of the NuCypher contracts, which is like a signal that the calling Ursula is online.

As for fees, Ursula collects part of the Ether locked by Alice during the policy's duration in proportion to the number of periods up to that point in which Ursula has confirmed her online status.

\subsection{Problems with Current Reward Computation Approach}
The current approach of computing Ursula's inflation rewards and service fees suffers from two
main problems:
\begin{itemize}
\setlength{\itemsep}{0pt}
\item The rewards computation (both fees and inflation) is agnostic to the number of 
requests Ursula serves. Thus, an active Ursula who may serve a huge number of 
re-encryption requests, and one who does not receive any requests (or a
malicious/lazy Ursula that does not answer Bob's requests), will 
both collect the same amount of rewards if they hold identical policies.

\item Confirming being online is flawed in the sense that this function does 
not require any input or proofs from Ursula on providing the service. Ursula 
can stay offline and not respond to Bobs' requests, but come online merely to call the confirm activity
function. This allows Ursula to collect both inflation rewards 
and fees without doing any work. Even worse, Ursula will be able to get her stake back once she unlocks its her stake (i.e., when policies being managed by Ursula expire). 
\end{itemize}

\subsection{Problem Statement}
The confirm activity problem is defined differently based on the stage of the 
NuCypher network. In early network operation, when inflation rewards are 
still distributed, we are concerned with the availability of Ursulas and being willing to 
serve all requests coming from Bob. In other words, regardless of the number of 
requests served, the rewards value will be computed based on the period during which Ursula 
is online and well-behaving. While in later stages, when inflation rewards disappear 
and only fees exist, confirm activity will be tied to providing the re-encryption 
service in the sense that the payment will be computed based on the amount of 
service provided. Thus, Ursula needs to confirm its activity by proving that she served 
a given number of distinct re-encryption requests during a given period. To make the distinction 
clear, we refer to the first as confirm availability, and for the second as confirm 
service activity.

>>>>

\section{Introduction}
\label{intro}
The NuCypher network~\cite{nucypher,egorov2017nucypher} is a decentralized key management 
system, encryption, and access control service. It uses threshold proxy re-encryption, namely, the 
Umbral scheme~\cite{umbral2018}, to delegate access to encrypted 
documents through a public network. This network is composed of a set of semi-trusted 
re-encryption service-providers, or Ursulas, that implement access control policies created by data 
owners, or Alices. Alice supplies each Ursula with re-encryption keys allowing a quorum of Ursulas to transform 
ciphertexts encrypted under Alice's public key into ciphertexts encrypted under the delegatee's, or Bob's,
public key. This enables the latter to decrypt the ciphertext without revealing anything about the
decryption keys or the raw data to the intermediate service-providers.

Joining the NuCypher network is governed by consensus rules defining the service setup
and the monetary incentives paid to provide the service. In order to join the 
system, Ursula needs to stake an amount of NU tokens (the native token of the network) for a specific period
which will be released when the pre-specified staking period is over. Alice chooses an
Ursula to hold an access control policy with a probability proportional to the stake this Ursula 
pledged in the system. Therefore, the stake value influences the service load an Ursula
may receive. This stake is also used to punish Ursula financially, by forfeiting part 
of it for detectable malfeasance.

Alice uses the network by creating a policy to be implemented by a 
set of Ursulas. This policy specifies the re-encryption key fragments each Ursula will
need to answer requests coming from Bob(s), as well as the duration of the policy, which 
is basically the timeframe during which Bob is authorized to access Alice's data.  Furthermore,
Alice will lock an amount of Ether into the policy contract to be used to pay Ursulas for the re-encryption 
service. As noted, Alice is not exposed to the NU token. All that she needs is an Ethereum
wallet, awareness of the NuCypher network architecture to select Ursulas, and knowledge of the
NuCypher rules of preparing access control policies.

Bob, on the other hand, does not deal with currency in the system at all. He interacts with the storage 
network to retrieve the encrypted data, and with Ursulas in the NuCypher network to request the
re-encryption service.

\subsection{Monetary Incentives in the NuCypher Network}
Ursulas are rewarded for their re-encryption service by using two sources; the first is the service fees collected from the policy owner Alice, while the second is a subsidy in the form of newly minted NU tokens distributed on a schedule enforced by the NuCypher protocol. The latter will be provided during the early stage of the network operation to encourage service-provider participation and sustain their operations in lieu of a mature fee market.

Currently, the subsidy size in each round or period is computed for each Ursula based on the size of her stake and duration of commitment to the network, and provided that she confirms to be online during this round. Confirming the status of being online is done by calling a simple function in one of the NuCypher contracts, which is like a signal that the calling Ursula is online. Similarly, for fees, Ursula collects part of the Ether locked by Alice during the policy's duration in proportion to the number of periods up to that point in which Ursula has confirmed her online status.

\subsection{Problems with Current Reward Computation Approach}
Although rewards computation and activity monitoring are reasonable for the first iteration of the network, we acknowledge that it suffers from two main problems:
\begin{itemize}
\setlength{\itemsep}{0pt}
\item The revenue computation (both fees and subsidy) is agnostic to the number of requests Ursula serves. Thus, an active Ursula who may serve a huge number of re-encryption requests, and one who does not receive any requests (or more importantly, a malicious/lazy Ursula that does not answer Bob's requests), will both collect the same amount of revenue if they hold identical policies.

\item Confirming being online is flawed in the sense that this function does not require any input or proofs from Ursula on providing the service. Ursula can stay offline the majority of the time and not respond to Bobs' requests, then come online merely to call the confirm activity function. This allows Ursula to collect both subsidy and fees without doing all (or even most) of the necessary work. Even worse, Ursula will be able to get her stake back once it unlocks.
\end{itemize}

Therefore, we need to devise a secure, non-gameable technique that confirms Ursula's availability and service activity. Then we need to adapt the subsidy and fee computation accordingly to factor in the amount of delivered service, and potentially punish Ursulas if it is insufficient. We introduce these topics in the remainder of the section.

\subsection{Problem Statement}
The confirm activity problem is defined differently based on the stage of the network operation. In the first 5 to 8 years after launch, when subsidy rewards are 
still distributed, we are concerned with the availability of Ursulas and their willingness to 
serve all requests coming from Bob. In other words, regardless of the number of requests served, the revenue total value (both subsidy and fees) will be computed based on the length of time during which Ursula 
is online and well-behaved. In later stages, when subsidies disappear 
and the only revenue comes from fees, confirm activity will be tied to providing the re-encryption 
service, in the sense that the payment will be partially computed based on the amount of 
service provided. This requires Ursula to confirm its activity by proving that she served 
a given number of distinct re-encryption requests during a given period. To make the distinction 
clear, we refer to the first as \emph{confirm availability}, and for the second as \emph{confirm 
service activity}.
